### 2015-03-02 fundamentals/conclusion.tex
To clarify phrasing as suggested by @flanflanagan

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
uncertain provenance, and restricted customizability, \Cyclus emphasizes an
open access and development strategy.  Open development, with transparent
publication of the source code, not only provides much-needed accessibility,
but also enables transparency and community oversight.

>>>>

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
open strategy for access and development.  This open strategy, with transparent
publication of the source code, not only provides much-needed accessibility,
but also enables transparency and community oversight.
